% \chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{thebibliography}{9}
\section*{Papers}

\bibitem{hairseg1}
Yongzhe Yan,
\textit{Human Hair Segmentation In The Wild Using Deep Shape Prior}, Computer Vision and Pattern Recognition 2019.

\bibitem{fpn}
Tsung-Yi Lin,
\textit{Feature Pyramid Networks for Object Detection}, Computer Vision and Pattern Recognition 2017.

\bibitem{densenet}
Gao Huang,
\textit{Densely Connected Convolutional Networks}, Computer Vision and Pattern Recognition 2017.

\bibitem{deeplabv3}
Liang-Chieh Chen,
\textit{Rethinking Atrous Convolution for Semantic Image Segmentation}, European Conference on Computer Vision 2018.

\bibitem{deeplabv3plus}
Liang-Chieh Chen,
\textit{Encoder-Decoder with Atrous Separable Convolution for Semantic Image Segmentation}, European Conference on Computer Vision 2018.

\bibitem{pspnet}
H. Zhao,
\textit{Pyramid Scene Parsing Network}, Conference on Computer Vision and Pattern Recognition 2018.

\bibitem{hairseg2matting}
Alex Levinshtein,
\textit{Real-time deep hair matting on mobile devices}, Conference on Computer and Robot Vision 2018.

\bibitem{resnet}
Kaiming He, Xiangyu Zhang, Shaoqing Ren, Jian Sun,
\textit{Deep Residual Learning for Image Recognition},
Computer Vision and Pattern Recognition 2016.

\bibitem{uml}
Ambler, S. W.
\textit{The Elements of UML(TM) 2.0 Style}, Cambridge University Press.

\bibitem{mnasnet}
Mingxing Tan,
\textit{MnasNet: Platform-Aware Neural Architecture Search for Mobile}, Conference on Computer and Robot Vision 2019.

\bibitem{mobiledets}
Yunyang Xiong,
\textit{MobileDets: Searching for Object Detection Architectures for Mobile
Accelerators}, Conference on Computer and Robot Vision 2021.

\bibitem{maskrcnn}
Kaiming He,
\textit{Mask R-CNN}, International Conference on Computer Vision 2017.

\bibitem{albumentations}
A. Buslaev,
\textit{Albumentations: fast and flexible image augmentations}, arXiv:1809.06839.

\bibitem{carbonemission}
WRAP,
\textit{Valuing Our Clothes}, The Cost of UK Fashion 2017.


\bibitem{deepfashion2}
Yuying Ge,
\textit{DeepFashion2: A Versatile Benchmark for Detection, Pose Estimation, Segmentation and Re-Identification of Clothing Images}, 
Computer Vision and Pattern Recognition 2019.

\bibitem{unet}
O. Ronneberger, P. Fischer, T. Brox,
\textit{U-Net: Convolutional Networks for Biomedical Image Segmentation}, 
International Conference on Medical Image Computing and Computer-Assisted Intervention 2015.


\bibitem{squeezenet}
Forrest N. Iandola,
\textit{U-Net: Convolutional Networks for Biomedical Image Segmentation}, 
International Conference on Medical Image Computing and Computer-Assisted Intervention 2015.


\bibitem{mnasnet}
M. Tan, B. Chen, R. Pang, V. Vasudevan,
\textit{Mnasnet: Platform-aware neural architecture search for mobile}, Computer Vision and Pattern Recognition 2019.

\bibitem{mobilenetv1}
AG. Howard, M. Zhu, B. Chen, D. Kalenichenko,
\textit{MobileNets: Efficient Convolutional Neural Networks for Mobile Vision Applications}, Computer Vision and Pattern Recognition 2019.


\bibitem{mobilenetv2}
Mark Sandler,
\textit{MobileNetV2: Inverted Residuals and Linear Bottlenecks}, arXiv:1704.04861.

\bibitem{openglpipeline}
S. Türkmen,
\textit{Scene Understanding Through Semantic Image Segmentation in Augmented Reality}, urn.fi/URN:NBN:fi:oulu-201906262666.

\bibitem{segnet}
Vijay Badrinarayanan,
\textit{SegNet: A Deep Convolutional Encoder-Decoder Architecture for Image Segmentation}, arXiv:1511.00561.

\bibitem{vgg}
Karen Simonyan, Andrew Zisserman,
\textit{Very Deep Convolutional Networks for Large-Scale Image Recognition}, 	arXiv:1409.1556.

\bibitem{thundernet}
Zheng Qin,
\textit{ThunderNet: Towards Real-time Generic Object Detection}, 		arXiv:1903.11752.

\section*{Websites}

\bibitem{jetpack}
https://developer.android.com/jetpack

\bibitem{qnnpack}
https://engineering.fb.com/2018/10/29/ml-applications/qnnpack/

\bibitem{androiddev}
https://developer.android.com/guide/topics/graphics/opengl

\bibitem{cs231n}
http://cs231n.github.io/neural-networks-1/

\bibitem{platformprediction}
https://cloud.google.com/ai-platform/prediction/docs

\bibitem{cloudfunctions}
https://cloud.google.com/blog/products/ai-machine-learning/how-to-serve-deep-learning-models-using-tensorflow-2-0-with-cloud-functions

\bibitem{googlecloudml}
https://cloud.google.com/ai-platform

\bibitem{tfserving}
https://github.com/tensorflow/serving




\end{thebibliography}
