\section{Objective and Contributions}

The thesis focuses on creating an Android app for the beauty field, aiming at smoothness and efficiency. By providing a real-time interaction experience, users see immediate feedback on objects they are tracking (at here are hair and clothes). In detail, users can preview images taken from cameras with hair or clothes being recolored and select a color as they like. Afterward, users are able to save or share images with hair and clothes recolored into storage. As a part of this thesis study, it is to research two crucial components: a fast on-device running model and a well-designed mobile app. Later, the problem in combining these two components is also seriously raised and tackled in my thesis. All in all, real-time performance on a wide variety of mobile devices is prioritized, while pixel-perfect masks may not be provided. \par
There are two main contributions of the thesis: a real-time beauty camera app running on Android and two deep learning models adapted for smartphones. About the app, it is designed with ten basic use cases, two of them are main features, namely Clothes Camera and Hair Camera. The real-time camera based on the CameraX framework achieves the speed of 60 FPS. In terms of masks rendering, I propose two methods (Bitmap and OpenGL), bringing about a good enough user experience. For rendering hair and clothes masks, it takes 24ms with OpenGL and slower with Bitmap. About the hair and clothes segmentation models, these two models achieve  86\% IoU on average. \par