\section{Motivation}
It is true that the clothing industry is in the top-4 most lucrative fields and often accounts for a significant portion of personal expenditures. People nowadays want to look good and expect higher at their outfits as the standard of living rises across the world. As a result, many find their preferred models, cuts, and styles of clothing but do not know what colors are the most well-suit to buy. These colors must flatter your skin tone or match with accessories’ tones. For a good outfit, pieces of clothes should not have any pair of complementary colors such as blue vs. orange, red vs. green. Usually, these color theories are well understood by stylists and fashionistas.
\par
Nevertheless, in case they choose a wrong color, many consequences might arise from that. Clothing that is not preferable is less likely to be worn, or more seriously, be discarded. Furthermore, it would form consumerism among society when people have not figured out suitable outfits, consequently increasing our environmental footprint. According to a report, the apparel industry's environmental impact, which is calculated throughout the entire life cycle of clothing, occupied 20\% of global water waste and 10\% of global carbon emission \cite{carbonemission}. Selecting clothes color visually on mobile phones is incredibly beneficial to the fashion industry.\par

Both women and men wear their hair in a variety of styles; each haircut can be dyed to many colors. With a multitude of colors, people always are often confused about commit a color from the wide variety available to them. 
\par
Considering the reasons mentioned earlier, there exists a need for a beauty app that helps the client to save time and effort in choosing hair and clothes color. Additionally, hair segmentation information can not only advance recommendation systems, but it is also used for a variety of applications, such as photo editing, make-up changes, and face detection. Further uses of clothing segmentation information appear on virtual try-on, clothing retrieves system, all of which are valuable applications for everyone in daily life.
\par