% target: 6 pages
\mychapter{1}{CHAPTER 1. INTRODUCTION}\label{ch:chap1}
\graphicspath{{./chapter1/image/}}

Recommendation systems have been applied in a vast range of industries, ranging from retail to healthcare, and it is undoubtedly getting more and more popularized in the next few decades. Many recommender systems leveraged by artificial intelligence has reinforced users’ selection and brings about superhuman solutions. In such a background, a hair and clothes color recommendation system that helps them select the most suitable color is in desire of society.  Hair and cloth segmentation models are addressed as the core of this thesis; they, in this study, are proposed and assessed. From that, the thesis proposes a prototype for beauty apps, including use-case analysis, interface and architecture design. Afterward, real-time hair and cloth recoloring application for mobile devices is developed and finally evaluated. \par

\input{./chapter1/chapter1_1_motivations.tex}
\input{./chapter1/chapter1_2_problem_background.tex}
\input{./chapter1/chapter1_3_objectives_contributions.tex}
\input{./chapter1/chapter1_4_difficulties.tex}


\section{Thesis structure}

There are totally five chapters in this thesis proceeded as follows. \par 
\textbf{Chapter 1: Introduction.} This chapter gives an overview of the thesis work, presents reasons and motivations of the work. Besides, some lately advancements in the field of semantic learning, smartphone deployment is briefly introduced. After this chapter, readers get a view of difficulties in hair and clothes segmentation, aside from objectives that the thesis follows.  \par
\textbf{Chapter 2: Background.} This chapter firstly introduces some convolutional neural networks that have been deployed on mobile devices, along with their specific applications. Secondly, Android and a few libraries are presented; it is also mentioned the reasons why they are used. Finally, tools for model deployment are given basic understand with TFLite is the core. TFLite is described with model optimization and converter.  \par
\textbf{Chapter 3: Method.} 
This chapter explains the architecture of the proposed model, the app pipeline. For the DNN, it is also explained the reasons why the architecture is chosen. For the app, we provide a brief introduction of hardware accelerator and TFLite backend support. At last, two rendering methods are presented. \par
\textbf{Chapter 4: Experiments and Result.} This chapter indicates experiments conducted on both the app and the model, gives quantitative results after that. Finally, this chapter concludes the thesis and suggests future work.\par